Improved association in a classical density functional theory for water

### 2014-01-16 papers/water-saft/paper.tex
Changes to water paper Tested on knightley. Took 0:14.83.

\begin{abstract}
We present a modification to our recently published SAFT-based classical
density functional theory for water.
%
We have recently developed and tested a functional for the averaged
radial distribution function at contact of the hard-sphere fluid
that is dramatically more accurate at interfaces than earlier
approximations.
%
We now incorporate this improved functional into the association term
of our free energy functional for water, improving its description of
hydrogen bonding.
%
We examine the effect of this improvement by studying two hard solutes(a
hard hydrophobic rod and a hard sphere) \fixme{and a Lennard-Jones solute.}
%
The improved functional leads to a moderate change in the density
profile and a large decrease in the number of hydrogen bonds broken in
the vicinity of the hard solutes.  
%
We find an improvement of the radial distribution for a Lennard-Jones
Krypton atom in water.
\end{abstract}
\maketitle

@@

Finally, in order to compare with experimental results, we examined
the hydration of Krypton.  Figure~\ref{fig:g-Kr} shows... demonstrate
an improved agreement with experiment.  \fixme{describe this}

@@

\begin{figure}
\begin{center}
\includegraphics[width=3.5in]{figs/Kr-278K-densities}
\end{center}
\caption{ $g$ for Kr and water at low temperature ($5^\circ$ C) and high
  pressure (110 bar).}
\label{fig:g-Kr}
\end{figure}

We have modified the classical DFT for water developed by
Hughes~\emph{et al.}~\cite{hughes2013classical} with the more accurate
radial distribution function at contact developed by Schulte~\emph{et
  al.}~\cite{schulte2012using}, which affects the predicted hydrogen
bonding between water molecules.  We found that while this
modification has a relatively mild effect on the free energy and
density profiles, it predicts fewer broken hydrogen bonds around
hard hydrophobic solutes and at aqueous interfaces.  \fixme{add in
  improvement demonstrated...}

>>>>

\begin{abstract}
We present a modification to our recently published SAFT-based classical
density functional theory for water.
%
We have recently developed and tested a functional for the averaged
radial distribution function at contact of the hard-sphere fluid
that is dramatically more accurate at interfaces than earlier
approximations.
%
We now incorporate this improved functional into the association term
of our free energy functional for water, improving its description of
hydrogen bonding.
%
We examine the effect of this improvement by studying two hard solutes
(a
hard hydrophobic rod and a hard sphere) and a Lennard-Jones
approximation of a krypton atom solute.
%
The improved functional leads to a moderate change in the density
profile and a large decrease in the number of hydrogen bonds broken in
the vicinity of the hard solutes.  
%
We find an improvement of the partial radial distribution for a
krypton atom in water when compared with experiment.
\end{abstract}
\maketitle

@@

Finally, in order to compare with experimental results, we examined
the hydration of Krypton.  We use a Lennard-Jones potential with
values $\epsilon = .9518$\fixme{units} and $\sigma = 3.42 \AA$ with mixing rules
and values from\cite{paschek2004temperature} where the water
parameters are based on SPC calculations. Figure~\ref{fig:g-Kr} shows a
comparison of the krypton-oxygen partial radial
distribution($g_{Kr-O}$) from the functional in this work and on
created from the functional of \hughesetal\ with experiment
\cite{bowron1998hydrophobic}.  The new functional shows an improvement
in the height of the first peak, and the general shape of $g_{O-Kr}$
compare to that of \hughesetal \

@@

\begin{figure}
\begin{center}
\includegraphics[width=3.5in]{figs/Kr-278K-densities}
\end{center}
\caption{ The Kr-O partial radial distribution function at low
  temperature ($5^\circ$ C) and high pressure (110 bar) in the limit
  of low concentration of krypton in water. The dashed blue line is
  computed using using the functional from \hughesetal, the solid red
  line is this work, and the black dotted line is from experiment
  \cite{bowron1998hydrophobic}. }
\label{fig:g-Kr}
\end{figure}

We have modified the classical DFT for water developed by
Hughes~\emph{et al.}~\cite{hughes2013classical} with the more accurate
radial distribution function at contact developed by Schulte~\emph{et
  al.}~\cite{schulte2012using}, which affects the predicted hydrogen
bonding between water molecules.  We found that while this
modification has a relatively mild effect on the free energy and
density profiles, it predicts fewer broken hydrogen bonds around
hard hydrophobic solutes and at aqueous interfaces.
%
The improved functional does indeed show better agreement with
experiment when used to compute the partial radial distribution
function of a krypton atom dissolved in water.
